Generalized spaces for constructive algebra

### 2020-01-08 slides-herrsching2019.tex
more precision

\begin{frame}{Sheaf semantics}
  \justifying\small
  Let~$X$ be a locale. We recursively define what it means for a
  \hil{first-order formula over an open~$U$ of~$X$} to be forced:
  \[ \footnotesize\renewcommand{\arraystretch}{1.08}\begin{array}{@{}l@{\ \ }c@{\ \ }l@{}}
  U \models \top &\Ll& \text{true} \\
  U \models \bot &\Ll& \hcancel{\text{false}}{0pt}{3pt}{0pt}{-2pt}\ U = \bot \\
  U \models s = t &\Ll& \text{$s = t$ when evaluated as elements of~$F(U)$} \\
  U \models \varphi \wedge \psi &\Ll&
  \text{$U \models \varphi$ and $U \models \psi$} \\
  U \models \varphi \vee \psi &\Ll&
  \hcancel{\text{$U \models \varphi$ or $U \models
  \psi$}}{0pt}{3pt}{0pt}{-2pt}\ \text{there exists a covering $U = \bigvee_i U_i$} \\
  && \quad\quad\text{such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$} \\
  U \models \varphi \Rightarrow \psi &\Ll&
  \text{for all~$V \leq U$: }
  \text{$V \models \varphi$ implies $V \models \psi$} \\
  U \models \forall s \? F\_ \varphi(s) &\Ll&
  \text{for all $V \leq U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$} \\
  U \models \exists s \? F\_ \varphi(s) &\Ll&
  \hcancel{\text{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  &&
  \text{there exists a covering $U = \bigvee_i U_i$ such that for all~$i$:} \\
  && \quad\quad \text{there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$}
  \end{array} \]
  \textbf{Theorem.} If~$U \models \varphi$ and if~$\varphi$ entails~$\psi$
  intuitionistically, then~$U \models \psi$.

@@

      \justifying
      \textbf{Proof.} See [Stacks Project].
      \medskip

>>>>

\begin{frame}{Sheaf semantics}
  \justifying\small
  Let~$X$ be a locale. We recursively define what it means for a
  \hil{first-order formula over an open~$U$ of~$X$} to be forced:
  \[ \footnotesize\renewcommand{\arraystretch}{1.08}\begin{array}{@{}l@{\ \ }c@{\ \ }l@{}}
  U \models \top &\Ll& \text{true} \\
  U \models \bot &\Ll& \hcancel{\text{false}}{0pt}{3pt}{0pt}{-2pt}\ U = \bot \\
  U \models s =_F t &\Ll& \text{$s = t$ when evaluated as elements of~$F(U)$} \\
  U \models \varphi \wedge \psi &\Ll&
  \text{$U \models \varphi$ and $U \models \psi$} \\
  U \models \varphi \vee \psi &\Ll&
  \hcancel{\text{$U \models \varphi$ or $U \models
  \psi$}}{0pt}{3pt}{0pt}{-2pt}\ \text{there exists a covering $U = \bigvee_i U_i$} \\
  && \quad\quad\text{such that for all~$i$: $U_i \models \varphi$ or $U_i \models \psi$} \\
  U \models \varphi \Rightarrow \psi &\Ll&
  \text{for all~$V \leq U$: }
  \text{$V \models \varphi$ implies $V \models \psi$} \\
  U \models \forall s \? F\_ \varphi(s) &\Ll&
  \text{for all $V \leq U$ and sections~$s_0 \in F(V)$: $V \models \varphi(s_0)$} \\
  U \models \exists s \? F\_ \varphi(s) &\Ll&
  \hcancel{\text{there exists $s_0 \in F(U)$ such that $U \models \varphi(s_0)$}}{0pt}{3pt}{0pt}{-2pt} \\
  &&
  \text{there exists a covering $U = \bigvee_i U_i$ such that for all~$i$:} \\
  && \quad\quad \text{there exists~$s_0 \in F(U_i)$ such that $U_i \models \varphi(s_0)$}
  \end{array} \]
  \textbf{Theorem.} If~$U \models \varphi$ and if~$\varphi$ entails~$\psi$
  intuitionistically, then~$U \models \psi$.

@@

      \justifying
      \textbf{Proof.} See \href{https://stacks.math.columbia.edu/tag/051Q}{[Stacks Project]}.
      \medskip
